### 2015-05-14 writing/SNLI paper/corpus.tex
Paper template

@@

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Validated pairs \& 53,852
Consensus label $\ne$ original label \& 8.5\%
No consensus label $\ne$ \& 2.1\%
Unanimous consensus \& 57.7\%

    \bottomrule
  \end{tabular}
\caption{\label{b-table}Key statistics for the validated sentence pairs.} 
\end{table}

>>>>

\subsection{Grounding with imagined images}

\subsection{Data collection}

\subsection{Data validation}

\subsection{Statistics}

Abstract (CP)

Intro (CP)

The corpus
- Why we use our wacky sort of grounding (CP)
- MTurk prompts, validation strategy, and other details about collection (Sam)
- Statistics (Sam)

Using the corpus as a platform for evaluation
- Non-neural baselines: methods and results (Gabor)
- RTE system(s): methods and results (Gabor)
- An NN architecture for evaluating sentence embedding models through entailment (Sam)
- NN model evaluations: methods and results (Sam)
- Discussion (Sam)

@@

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Validated pairs \& 53,852\\
Consensus label $\ne$ original label \& 8.5\%\\
No consensus label $\ne$ \& 2.1\%\\
Unanimous consensus \& 57.7\%\\
    \bottomrule
  \end{tabular}
\caption{\label{b-table}Key statistics for the validated sentence pairs.} 
\end{table}
